SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/acknowledgments.tex
and patrick
Martins final comments

My advisers Martin Giese and Arild Waaler deserves a big thanks for
kickstarting the project, help adjusting its course over the years and
thorough and enlightened criticism of manuscripts prior to submission.

@@

It is also a pleasure to thank the entire Semantic Web community for
their openness and welcoming attitude. Whether you come as a hacker
or want to pursue standardisation, you are likely to meet people like
Dan Brickley, Charles Nevile, Andy Seaborne, Steve Harris, Phil Archer
or Ivan Herman, all of whom have been important for my understanding
of the Semantic Web. The academic community, with their important ISWC
and ESWC conferences are equally welcoming, and has culture of sharing
insight that many other academic communities would envy. Many thanks
are due to Oscar Corcho for first integrating me into the community,
Maria-Esther Vidal and Jacco van Ossenbruggen for encouraging me to
further pursue the speculations around the role of empirical methods,
and general support. Jürgen Umbrich and Axel Polleres deserves a big
thanks for welcoming me in Vienna and many discussions.

@@

The Perl community have also been important in developing the ideas
and the code of this thesis. In addition to Gregory Todd Williams, I
would like to thank Toby Inkster, Chris Prather, Kip Hampton, Robin
Berjon, Shawn M.  Moore, Michael Nachbaur and Jonas Smedegaard.

>>>>

My advisers Martin Giese and Arild Waaler deserve a big thanks for
kickstarting the project, help adjusting its course over the years and
thorough and enlightened criticism of manuscripts prior to submission.

@@

It is also a pleasure to thank the entire Semantic Web community for
their openness and welcoming attitude. Whether you come as a hacker
or want to pursue standardisation, you are likely to meet people like
Dan Brickley, Charles Nevile, Andy Seaborne, Steve Harris, Phil Archer
or Ivan Herman, all of whom have been important for my understanding
of the Semantic Web. The academic community, with their important ISWC
and ESWC conferences are equally welcoming, and has culture of sharing
insight that many other academic communities would envy. Many thanks
are due to Oscar Corcho for first integrating me into the community,
Maria-Esther Vidal and Jacco van Ossenbruggen for encouraging me to
further pursue the speculations around the role of empirical methods,
and general support. Jürgen Umbrich and Axel Polleres deserve a big
thanks for welcoming me in Vienna and many discussions.

@@

The Perl community have also been important in developing the ideas
and the code of this thesis. In addition to Gregory Todd Williams, I
would like to thank Toby Inkster, Patrick Hochstenbach, Chris Prather,
Kip Hampton, Robin Berjon, Shawn M.  Moore, Michael Nachbaur and Jonas
Smedegaard.
